---
title: "MachinePeerGraded"
author: "Prajwal Dutta"
date: "10/21/2020"
output: html_document
---

## Summary

Nowadays with accelerometers wecan get accccurate data on how people exercise.This project we want to use data of 6 participants for such analysis.


## Preprocessing 

Loading training and testing sets 

```{r DataLoading, message = FALSE}
library(caret)
setwd("C:/Users/MAHE/Documents/Archit/R progs/Practical-Machine-Learning")
trainURL <- "http://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
testURL <- "http://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
traini <- read.csv(url(trainURL))
testi <- read.csv(url(testURL))
label<- createDataPartition(traini$classe, p = 0.7, list = FALSE)
trainpraj <- traini[label, ]
testpraj <- traini[-label, ]
```

We remove NA variable 

```{r DataCleaning}
NZ<- nearZeroVar(trainpraj)
trainpraj<- trainpraj[ ,-NZ]
testpraj <- testpraj[ ,-NZ]
label<- apply(trainpraj, 2, function(x) mean(is.na(x))) > 0.95
trainpraj <- trainpraj[, -which(label, label== FALSE)]
testpraj <- testpraj[, -which(label, label == FALSE)]
trainpraj <- trainpraj[ , -(1:5)]
testpraj <- testpraj[ , -(1:5)]
```

## Exploratory analysis

We nowlook atcorrelation plot. 

```{r CorrelationPlot, fig.width=10, fig.height=9}
library(corrplot)
corrMat <- cor(trainpraj[,-54])
corrplot(corrMat, method = "color", type = "lower", tl.cex = 0.7, tl.col = rgb(0,0,0))
```

plot above shows that the darker area has more ccorelation than rest

## Prediction Models

We need Decision Tree, Random Forest and Generalized Boosted model, methods to model our training set 

### Decision Tree

```{r DecisionTree, message = FALSE, warning = FALSE, fig.width=15, fig.height=10}
library(rpart)
library(rpart.plot)
library(rattle)
set.seed(13908)
modelpraj <- rpart(classe ~ ., data = trainpraj, method = "class")
fancyRpartPlot(modelpraj)
predictpraj <- predict(modelpraj, testpraj, type = "class")
confMatD <- confusionMatrix(predictpraj, testpraj$classe)
confMatD
```

### Random Forest

```{r RandomForest, message = FALSE}
library(caret)
set.seed(13908)
control <- trainControl(method = "cv", number = 3, verboseIter=FALSE)
modelpra <- train(classe ~ ., data = trainpraj, method = "rf", trControl = control)
modelpra$finalModel
predictpra <- predict(modelpra, testpraj)
confMatR <- confusionMatrix(predictpra, testpraj$classe)
confMatR
```

### Generalized Boosted Model

```{r GBM, message = FALSE}
library(caret)
set.seed(13908)
control <- trainControl(method = "repeatedcv", number = 5, repeats = 1, verboseIter = FALSE)
modelpr <- train(classe ~ ., data = trainpraj, trControl = control, method = "gbm", verbose = FALSE)
modelpr$finalModel
predictpr <- predict(modelpr, testpraj)
confMatGB <- confusionMatrix(predictpr, testpraj$classe)
confMatGB
```

Random forest is selected

## Test set outputs

```{r TestSetPrediction, messages = FALSE}
predictpra <- predict(modelpra, testi)
predictpra
```